---
title: "Full analysis"
author: "Miguel Juliá"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r load libraries}
suppressMessages({
library(splatter)
library(Seurat)
library(msigdbr)
library(singleseqgset)
library(heatmap3)
library(GEOquery)
library(Seurat) 
library(scater)
library(SingleCellExperiment)
library(viridisLite)
library(viridis)
library(clustree)
library(MAST)
library(destiny)
# library(ggbeeswarm)
library(ggthemes)
library(dplyr)
library(tidyr)
library(Seurat)
library(stringr)
library(colorRamps)
library(colorRamps)
library(pheatmap)
library(RColorBrewer)
library(dplyr)
library(singleseqgset)
library(devtools)
library(zellkonverter)
library(knitr)
library(harmony)
library(SingleR) 
library(celldex)
})
```

```{r}
set.seed(101100)
```

Set working directory
```{r}

wd <- "/path/to/working/directory/Fibroblasts_IanireAstobiza"
setwd(wd)
data.folder <- file.path(wd)
```

Load data
```{r}

file <- "Annotation_Manual_Miguel_AC55_BPH.rds"
srat <- readRDS(file=file.path(data.folder, file))
```

Identify fibroblasts
```{r}

srat <- SetIdent(srat, value = "seurat_clusters")
DimPlot(srat, label = TRUE, repel = TRUE) + theme(legend.position="none")

srat <- SetIdent(srat, value = "annotation")
DimPlot(srat, label = T , repel = T, label.size = 3) + ggtitle('Annotation') + theme(legend.position="none")

srat <- SetIdent(srat, value = "orig.ident")
DimPlot(srat, label = T , repel = T, label.size = 3) + ggtitle('Sample origin') + theme(legend.position="none")

srat <- SetIdent(srat, value = "DF")
DimPlot(srat, label = T , repel = T, label.size = 3) + ggtitle('Doublets') + theme(legend.position="none")

# Assign mycelltype
srat <- SetIdent(srat, value = "annotation")
tmp <- as.character(srat$annotation)
tmp[ as.character(srat$annotation) == "3_Fibroblasts - Pericytes" ] <- "fibroblast"
tmp[ as.character(srat$annotation) == "4_Fibroblasts - Pericytes" ] <- "fibroblast"
srat$mycelltype <- tmp
rm(tmp)
srat <- SetIdent(srat, value = "mycelltype")
DimPlot(srat, label = T , repel = T, label.size = 3) + ggtitle('mycelltype') + theme(legend.position="none")
DimPlot(srat, label=F, cells.highlight= list(WhichCells(srat, idents = c( "fibroblast"))), cols.highlight = c("darkblue"), cols= "grey")

# Assign Fer's celltype classification
srat <- SetIdent(srat, value = "seurat_clusters")
tmp <- rep("NA", length(srat$seurat_clusters))
tmp[ srat$seurat_clusters == 0 ] <- "T/NK cell"
tmp[ srat$seurat_clusters == 1 ] <- "myeloid"
tmp[ srat$seurat_clusters == 2 ] <- "endothelial"
tmp[ srat$seurat_clusters == 3 ] <- "fibroblast"
tmp[ srat$seurat_clusters == 4 ] <- "fibroblast"
tmp[ srat$seurat_clusters == 5 ] <- "epithelial"
tmp[ srat$seurat_clusters == 6 ] <- "epithelial"
tmp[ srat$seurat_clusters == 7 ] <- "epithelial"
tmp[ srat$seurat_clusters == 8 ] <- "endothelial"
tmp[ srat$seurat_clusters == 9 ] <- "myeloid"
tmp[ srat$seurat_clusters == 10 ] <- "B cell"
tmp[ srat$seurat_clusters == 11 ] <- "epithelial"
tmp[ srat$seurat_clusters == 12 ] <- "epithelial"
tmp[ srat$seurat_clusters == 13 ] <- "mastocytes"
tmp[ srat$seurat_clusters == 14 ] <- "epithelial"
tmp[ srat$seurat_clusters == 15 ] <- "epithelial"
tmp[ srat$seurat_clusters == 16 ] <- "NA"
tmp[ srat$seurat_clusters == 17 ] <- "NA"
tmp[ srat$seurat_clusters == 18 ] <- "NA"
tmp[ srat$seurat_clusters == 19 ] <- "fibroblast"
tmp[ srat$seurat_clusters == 20 ] <- "endothelial"
srat$fer_classification <- as.factor(tmp)
rm(tmp)
srat <- SetIdent(srat, value = "fer_classification")
DimPlot(srat, label = F , repel = T, label.size = 3) + ggtitle('fer_classification') + theme(legend.position="none")
DimPlot(srat, label=F, cells.highlight= list(WhichCells(srat, idents = c( "fibroblast"))), cols.highlight = c("darkblue"), cols= "grey")

# Cell type annotation using SingleR
srat <- SetIdent(srat, value = "seurat_clusters")
hpca.ref <- celldex::HumanPrimaryCellAtlasData()
sce <- as.SingleCellExperiment(DietSeurat(srat))
sce
hpca.main <- SingleR(test = sce,assay.type.test = 1,ref = hpca.ref,labels = hpca.ref$label.main)
hpca.fine <- SingleR(test = sce,assay.type.test = 1,ref = hpca.ref,labels = hpca.ref$label.fine)
table(hpca.main$pruned.labels)
table(hpca.fine$pruned.labels)
srat@meta.data$hpca.main   <- hpca.main$pruned.labels
srat@meta.data$hpca.fine   <- hpca.fine$pruned.labels

srat <- SetIdent(srat, value = "hpca.main")
DimPlot(srat, label = T , repel = T, label.size = 3) + ggtitle('Tissue types Fibrolasts all')

list_fibroblasts <- WhichCells(srat, idents = c( "Fibroblasts"))
DimPlot(srat, label=F, cells.highlight= list(list_fibroblasts), cols.highlight = c("darkblue"), cols= "grey")




```


Find markers for each cluster, each assigned cell type, and assigned fibroblasts cluster
```{r}

srat <- SetIdent(srat, value = "annotation")
markers <- FindAllMarkers(srat)
write.table(markers, file = file.path(data.folder, "/markers/markers_annotation.tsv"), sep = "\t", row.names = T, col.names = T, quote = FALSE )

srat <- SetIdent(srat, value = "mycelltype")
markers <- FindAllMarkers(srat)
write.table(markers, file = file.path(data.folder, "/markers/markers_mycelltype.tsv"), sep = "\t", row.names = T, col.names = T, quote = FALSE )
markers <- FindMarkers(srat, ident.1 = c("fibroblast"))
write.table(markers, file = file.path(data.folder, "/markers/markers_fibroblast.tsv"), sep = "\t", row.names = T, col.names = T, quote = FALSE )

srat <- SetIdent(srat, value = "fer_classification")
markers <- FindAllMarkers(srat)
write.table(markers, file = file.path(data.folder, "/markers/markers_fer_classification.tsv"), sep = "\t", row.names = T, col.names = T, quote = FALSE )

```

Check fibroblast markers
```{r}
for (gene in c("FAP", "SPARC", "PDPN", "PDGFRA", "COL15A1", "CXCL12", "SOD2", "PI16", "CD34", "C3", "OGN", "CCL19", "CXCL9", "CD74", "CXCL1", "CXCL2", "CXCL3", "CXCL12", "APOD", "CD48", "CD3D", "TMEM158", "VEGFA", "NOTCH3", "HEY1", "MMP9", "BMP8A", "RGS5", "MCAM", "TAGLN", "MMP11", "COL1A2", "COL10A1", "COL11A1", "KIF26B", "MKI67", "CDK1", "IDO1", "MMP1")){
  print(FeaturePlot(srat, reduction = "umap", features = gene))
}

```


And what happens if we only take what they defined as fibroblasts

```{r}

srat <- SetIdent(srat, value = "mycelltype")
all.fibroblast.cl10 <- subset(x = srat, ident = c("fibroblast"))

all.fibroblast.cl10 <- SetIdent(all.fibroblast.cl10, value = "mycelltype")
DimPlot(all.fibroblast.cl10, label = F, repel = TRUE)

all.fibroblast.cl10 <- SetIdent(all.fibroblast.cl10, value = "seurat_clusters")
DimPlot(all.fibroblast.cl10, label = TRUE, repel = TRUE)

all.fibroblast.cl10 <- SetIdent(all.fibroblast.cl10, value = "hpca.main")
list_fibroblasts <- WhichCells(all.fibroblast.cl10, idents = c( "Fibroblasts"))
DimPlot(all.fibroblast.cl10, label=F, cells.highlight= list(list_fibroblasts), cols.highlight = c("darkblue"), cols= "grey")

all.fibroblast.cl10 <- SetIdent(all.fibroblast.cl10, value = "orig.ident")
DimPlot(all.fibroblast.cl10, label = F , repel = T, label.size = 3) + ggtitle('Sample origin')

all.fibroblast.cl10 <- ScaleData(all.fibroblast.cl10, verbose = FALSE, )
all.fibroblast.cl10 <- RunPCA(all.fibroblast.cl10, npcs = 50, verbose = FALSE)

all.fibroblast.cl10 <- RunHarmony(all.fibroblast.cl10, 
				group.by.vars = c("orig.ident"), 
				reduction = "pca", reduction.save = "harmony")
all.fibroblast.cl10 <- RunUMAP(all.fibroblast.cl10, reduction = "harmony", dims = 1:50)
all.fibroblast.cl10 <- FindNeighbors(object = all.fibroblast.cl10, reduction = "harmony")
all.fibroblast.cl10 <- FindClusters(all.fibroblast.cl10, resolution = c(0.2, 0.4, 0.6, 0.8, 1.0, 1.2))

all.fibroblast.cl10 <- SetIdent(all.fibroblast.cl10, value = "seurat_clusters")
DimPlot(all.fibroblast.cl10, reduction = "umap", label = TRUE, repel = TRUE)

all.fibroblast.cl10 <- SetIdent(all.fibroblast.cl10, value = "hpca.main")
DimPlot(all.fibroblast.cl10, reduction = "umap", label = TRUE, repel = TRUE) + theme(legend.position="none")

all.fibroblast.cl10 <- SetIdent(all.fibroblast.cl10, value = "hpca.main")
list_fibroblasts <- WhichCells(all.fibroblast.cl10, idents = c( "Fibroblasts"))
DimPlot(all.fibroblast.cl10, reduction = "umap", label=F, cells.highlight= list(list_fibroblasts), cols.highlight = c("darkblue"), cols= "grey")

# FeaturePlot(all.fibroblast.cl10, reduction = "umap", features = "CD105") ## Not available
for (gene in c("FAP", "SPARC", "PDPN", "PDGFRA", "COL15A1", "CXCL12", "SOD2", "PI16", "CD34", "C3", "OGN", "CCL19", "CXCL9", "CD74", "CXCL1", "CXCL2", "CXCL3", "CXCL12", "APOD", "CD48", "CD3D", "TMEM158", "VEGFA", "NOTCH3", "HEY1", "MMP9", "BMP8A", "RGS5", "MCAM", "TAGLN", "MMP11", "COL1A2", "COL10A1", "COL11A1", "KIF26B", "MKI67", "CDK1", "IDO1", "MMP1")){
  print(FeaturePlot(all.fibroblast.cl10, reduction = "umap", features = gene))
}

```


```{r}

all.fibroblast.cl10 <- SetIdent(all.fibroblast.cl10, value = "seurat_clusters")
markers <- FindAllMarkers(all.fibroblast.cl10)
write.table(markers, file = file.path(data.folder, "/markers/markers_fibroblast_clusters_onlyCluster10.tsv"), sep = "\t", row.names = T, col.names = T, quote = FALSE )

```



## 3. Map of expression in both types of data (whole tumor and fibroblasts) for indicated genes and signatures

Get signatures and genes

```{r}

library(xlsx)
setwd("/home/juliam/Documents/FernandoCalvo/scRNAseq_test/Signaures")

my_signatures <- read.xlsx("genes and signatures Miguel ASPA project v3.xlsx", 3, header = T)

# Genes not present: "LRRC15", "NOCHT3", "CTGF"
my_genes <- c("ASPA", "NAT8L", "FOLH1", "NAALADL2", "RIMKLB", "ACSS1", "ACSS2", "ACLY", "PALLD", "DKK3", "LOXL2", "ACTG2", "INHBA", "POSTN", "TAGLN", "ACTA2", "THBS1", "COL1A1", "IL6", "IL1A", "DCN", "CXCL12", "TGFBI", "ITGA11", "IGFBP3", "LOX", "NOX4", "WNT10A", "ITGA8", "TGFB1", "TGFB2", "TGFB3", "TGFBR1", "TGFBR2", "TGFBR3", "WNT5A", "MYL9", "LIF", "CXCL1", "CXCL2", "CCL2", "CALD1", "CD74")

setwd(wd)

my_signatures <- my_signatures[2:904,]

```


Signature expression bladder

```{r gene expression Bladder}

DefaultAssay(srat) <- "RNA"

Bladder.table <- data.frame(
  cluster = srat$seurat_clusters,
  annotation = srat$annotation,
  fer_classification = srat$fer_classification,
  prediction = srat$hpca.main
)

for (signature in colnames(my_signatures)){
  signature_name <- signature
  signature_genes <- my_signatures[signature]
  marker_gene_list <- signature_genes[!is.na(signature_genes)]
  
  marker_gene_list <- list(unlist(marker_gene_list))
  
  srat <- AddModuleScore(srat, features = marker_gene_list, name = signature_name)
  print(FeaturePlot(srat, features = paste0(signature_name,"1")))
  
  Bladder.table[signature_name] <- srat[[paste0(signature_name,"1")]]
}

for (gene_set in 0:(as.integer(length(my_genes) / 4))) {
  print(FeaturePlot(srat, features = my_genes[(gene_set*4+1):min((gene_set*4+1)+3,length(my_genes))]))
}

for (gene in my_genes){
  Bladder.table[gene] <- FetchData(srat, vars = gene)
} 

```



Signature expression bladder fibroblasts

```{r gene expression Bladder fibroblasts}

DefaultAssay(all.fibroblast.cl10) <- "RNA"

Bladder.fibroblast.table <- data.frame(
  cluster = all.fibroblast.cl10$seurat_clusters,
  annotation = all.fibroblast.cl10$annotation,
  fer_classification = all.fibroblast.cl10$fer_classification,
  prediction = all.fibroblast.cl10$hpca.main
)

for (signature in colnames(my_signatures)){
  signature_name <- signature
  signature_genes <- my_signatures[signature]
  marker_gene_list <- signature_genes[!is.na(signature_genes)]
  
  marker_gene_list <- list(unlist(marker_gene_list))
  
  all.fibroblast.cl10 <- AddModuleScore(all.fibroblast.cl10, features = marker_gene_list, name = signature_name)
  print(FeaturePlot(all.fibroblast.cl10, features = paste0(signature_name,"1")))
  
  Bladder.fibroblast.table[signature_name] <- all.fibroblast.cl10[[paste0(signature_name,"1")]]
}

for (gene_set in 0:(as.integer(length(my_genes) / 4))) {
  print(FeaturePlot(all.fibroblast.cl10, features = my_genes[(gene_set*4+1):min((gene_set*4+1)+3,length(my_genes))]))
}

for (gene in my_genes){
  Bladder.fibroblast.table[gene] <- FetchData(all.fibroblast.cl10, vars = gene)
} 

```


## 4. Expression matrix (average) so we can generate a heatmap or graph (gene and signatures)

I created the tables containing for every cell: normalised expression values per gene, signature value, cluster assigned, and celltype assigned.

Bladder

```{r heatmap Bladder}
write.csv(Bladder.table, file="markers/Bladder.table.rethinkingclustering.csv")

```

Bladder fibroblast

```{r heatmap Bladder fibroblast}

write.csv(Bladder.fibroblast.table, file="markers/Bladder.fibroblast.table.rethinkingclustering.csv")

```


## 5. For the BLCA dataset that we have normal and cancer tissue, expression matrix for gene and signtures of fibroblasts from normal and tumor

Added as extra field in previous tables.
